Dunnett's test

### 2024-06-20 text/22/definition-schoenfeld-residuals.Rmd
Update 2022 files, part 3

---
title: "Schoenfeld residuals"
author: "Steve Simon"
date: '2022-11-30'
output:
  html_document: default
category: Blog post
tags: Survival analysis
source: new
---

>>>>

---
title: "Schoenfeld residuals"
author: "Steve Simon"
date: '2022-11-30'
output:
  html_document: default
category: Blog post
tags:
- Survival analysis
source: new
page_update: complete
---

### 2024-06-20 text/22/dunnetts-test.Rmd
Update 2022 files, part 3

---
title: "Dunnett's test"
author: "Steve Simon"
date: '2022-07-04'
output:
  html_document: default
category: Blog post
tags: Analysis of means
source: new
---

>>>>

---
title: "Dunnett's test"
author: "Steve Simon"
date: '2022-07-04'
output:
  html_document: default
category: Blog post
tags:
- Analysis of means
source: new
page_update: complete
---
